What's in a name? On the automated topic naming of software maintenance activities

### 2010-03-05 icpc/icpc2010.tex
bibliography stuff
This is expiremental

\XXX{this table should have mysql}
\begin{table*}[h]
	\caption{Automatic topic labeling}
	\centering
	\label{tbl:wordlist}
\begin{tabular}{c|c|c|c}
\toprule
Measure &		 \textsf{exp1} &	 \textsf{exp2} &	 \textsf{exp3} \\
\midrule
Topics &			500		 &			500  	 & 		500  \\
Named topics &		281      &			125      &		328  \\
Unnamed topics &	139      &			295      &      92   \\
\bottomrule
\end{tabular}
\end{table*}

@@

\XXX{WRITE THIS}

@@

\bibliographystyle{IEEEtran}
\bibliography{icpc}

>>>>

\XXX{this table should have mysql}
\begin{table}
	\caption{Automatic topic labeling}
	\centering
	\label{tbl:wordlist}
\begin{tabular}{c|c|c|c}
\toprule
Measure &		 \textsf{exp1} &	 \textsf{exp2} &	 \textsf{exp3} \\
\midrule
Topics &			500		 &			500  	 & 		500  \\
Named topics &		281      &			125      &		328  \\
Unnamed topics &	139      &			295      &      92   \\
\bottomrule
\end{tabular}
\end{table}

@@

* Demonstrated that domain specific knowledge is valuable
* Demonstrated the feasibility of static approaches and supervised approaches
* Showed that non functional requirement pervade much many of the topics that are extracted

In conclusion we have demonstrated that static but domain specific knowledge can improve unsupervised labelling of extracted topics. Our \textsf{exp2} experiment had fewer terms but performed mostly just as well as \textsf{exp3} which used more general terms.

@@

\bibliographystyle{abbrv}
%\bibliographystyle{IEEEtran}
\bibliography{icpc}
